Pyg4ometry: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-08-28 public/paper/pyg4ometry.tex
Added Faraday cup
Stripped back what is required

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=7cm]{./diagrams/rapidModelling.pdf}
\caption{FLUKA input with an AST.}
\label{fig:region-ast}
\end{center}
\end{figure}

@@

\subsection{Disjoint unions}
A disjoint union in FLUKA is a union of two or more zones that are not
connected.  This is a valid construct in FLUKA but is explicitly
forbidden in Geant4 and must be removed during the conversion
process.  Disjoint unions are detected by checking for overlaps
between all zones within a union.

@@

\subsection{Example}

\subsection{TODO}
\begin{itemize}
\item disjoint subtractions?
\item quadric specialisation
\item second order lattice
\item Materials 
\end{itemize}
\section{GDML to FLUKA conversion}
It is relatively straight forward to convert Geant4 geometry to FLUKA. Each of the Geant4 solids can be mapped to a FLUKA CSG region.
Some solids in Geant4 directly map to a FLUKA body, others need a construction of a simple FLUKA CSG tree. Table~\ref{tab:geant2fluka}
lists the mapping between geant4 solids and the bodies used to compose a fluka region.

@@

\subsection{Outstanding issues}
There are still a few outstanding issues with Geant4/GDML to Fluka conversion.

\subsection{Example}

\subsection{TODO}
\begin{itemize}
\item Non-convex solids, convex decomposition (Polyhedron, Xtru, TwistedBox, TwistedTrap, TwistedTrd, TwistedTube)
\item Non-convex 2D section (GenericPolycone, GenericPolyhedra)
\item Scaled solid 
\item Placement scale 
\item Replica, Division, Parameterised
\item Materials 
\end{itemize}

@@

\subsection{Example}

\section{Interesting use cases}
Pyg4ometry is designed to be as flexible as possible and offer the user a wide range of usage styles and workflows. The following sections describe a selection of 
possible applications.

\subsection{Mixing geometry sources}
It is possible to mix different geometries from STL, STEP, GDML and FLUKA in single GDML file for use in Geant4 and ROOT.

\subsection{Modifying existing models}
Often existing CAD models have either missing details or too many details. Examples of too potentially superfluous detail are gaskets and bolts

\subsection{Overlap checking in geometry}
Often small errors in geometry cause unexpected RT code behaviour.

\section{Performance of converted geometry in Geant4}
Clearly for Geant4 geometry defined in pyg4ometry the performance is exactly the same as it the geometry was specified in C++ and linked against the Geant4
libraries. A comparison of the performance of converted CAD or FLUKA geometry compared with native Geant4 solids is required so a user can optimise the available
computing resources against the human resources (required to convert geometry). BDSIM is used to load the pyg4ometry generated files  and run basic simulations where 
high energy particles are

>>>>

\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=0.95\textwidth]{./model-scene/faradayCup2.pdf}
\caption{FLUKA input with an AST.}
\label{fig:region-ast}
\end{center}
\end{figure*}

@@

@@

\subsection{Discussion}
A disjoint union in FLUKA is a union of two or more zones that are not
connected.  This is a valid construct in FLUKA but is explicitly
forbidden in Geant4 and must be removed during the conversion
process.  Disjoint unions are detected by checking for overlaps
between all zones within a union.

\begin{itemize}
\item disjoint subtractions?
\item quadric specialisation
\item second order lattice
\item Materials 
\end{itemize}

\section{GDML to FLUKA conversion}
It is relatively straight forward to convert Geant4 geometry to FLUKA. Each of the Geant4 solids can be mapped to a FLUKA CSG region.
Some solids in Geant4 directly map to a FLUKA body, others need a construction of a simple FLUKA CSG tree. Table~\ref{tab:geant2fluka}
lists the mapping between geant4 solids and the bodies used to compose a fluka region.

@@

\subsection{Disjunctive normal form and degenerate surfaces}

\subsection{Disucssion}
There are still a few outstanding issues with Geant4/GDML to Fluka conversion.

\begin{itemize}
\item Non-convex solids, convex decomposition (Polyhedron, Xtru, TwistedBox, TwistedTrap, TwistedTrd, TwistedTube)
\item Non-convex 2D section (GenericPolycone, GenericPolyhedra)
\item Scaled solid 
\item Placement scale 
\item Replica, Division, Parameterised
\item Materials 
\end{itemize}

@@

\section{Complete simulation example}
Pyg4ometry is designed to be as flexible as possible and offer the user a wide range of usage styles and workflows. The following sections describe a selection of 
possible applications.
